Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-03 conclusion.tex
added three references.

>>>>

Impact of WMS on HEP foreshadows the importance of WMS for other experiments and
their computational campaign.

Titan has upwards of 93\%. Compare that with Blue Waters 80\% (XDMoD).

Role of abstractions. Important/critical. As platforms available to science
changes, both in terms of type of infrastructure (Summit) as well as Clouds.

This work is a starting point and represents our initial experience. However, 
this initial experience allows us to

Sets the basis for more optimized and studied operation points.
